%*******************************************
\section{Scope of Our Approach}
%*******************************************
This chapter elaborates on the determination of our scope to educate people about phishing. 
Here, we gather all of our choices and the corresponding reasoning for our defintion of our scope. 
These include the various classes of phishing and phishing learning techniques that we mentioned in \autoref{s:background} as well as new aspects.
Subsequently, we summarize the system requirements and what assumptions we had to make. 
Finally, the limitations of our work are stated.

%===========================================
\subsection{Coverage}
%===========================================
\label{s:coverage}
\begin{description}[leftmargin=0cm]
	\item[Deceptive Phishing as Phishing Technique:] As outlined in \autoref{s:phishing_general}, within the scope of this work we focus on deceptive phishing.
 In particular, we target the detection of phishing websites resp. phishing URLs.

	\item[Several Attack Channels:] In order to be independent from the source a link may originate from, we set our focus on the analysis of URLs before entering private data, i.e. on the website itself, such that any attack channel distributing a link to a fake website will be covered by our approach (cf. \autoref{s:phishing_general}).

	\item[Mass Phishing as Variation of Phishing:] We cover mass phishing, as already stated in \autoref{s:phishing_variations}.
 However, the URL checking can be applied in case of any variant, as long as the attack includes a website which lures the user into typing in his credentials.

	\item[URL Based Knowledge as Learning Content:] As argued in \autoref{s:content_classification} we believe that URL based knowledge gives the most reliable hint regarding its ``origin'', i.e. whether a URL in fact belongs to a legitimate website or not. This will be the focus of the learning content in our app.

	\item[Game and Quiz Based Learning as Communication Medium:] As discussed in \autoref{s:medium_classification}, we decided to develop a quiz game to create an incentive for the users and at the same time reach a large audience. 

	\item[After Click URL Analysis:] The analysis of a URL can follow before or after clicking on a link (if a link is involved), i.e. with a URL preview option or directly in the address bar. 
Analyzing the URL before clicking on it brings several benefits:

\begin{enumerate}
	\item \textit{No Malicious Download:} If a spoofed URL is detected before clicking on a link the potential download of  malicious software can be avoided. 
	\item \textit{Phisher Obtains No Information:} Recognizing the spoofed URL before visiting the website prevents the phisher from obtaining any information of the user. Such information includes, for example, the activeness and validity of the user's e-mail address. 
\end{enumerate}

On the other hand, the before click scenario has severe downsides:

\begin{enumerate}
	\item \textit{Redirects Not Recognizable:} Many links contain redirects. Such redirects, which can be malicious, are not recognizable before the click.
	\item \textit{Unavailability of URL Preview Functionality:} The URL preview functionality is generally available among various browsers. 
However, the stock e-mail client of Android, for example, does not provide the functionality of previewing the destination URL. 
Here, the only way to preview the URL is to apply a long press to the link, copy it into the clipboard, paste it somewhere else and then view it. 
Then, after the analysis the URL has to be sent to the browser.
As this involves too much effort, it is likely that no user will follow such a suggestion.
Another possibility would be to force e-mail applications to display plain text in general.
The problem with this is that this functionality is also highly dependent on the applied e-mail application and covering all possibilities would not feasible.
	\item \textit{Deception with URL Preview:} Browsers in general and several other e-mail clients provide options to display the destination URL of a link.
Yet, we believe that this should not be communicated to the user for two reasons.
First, we are elaborating on a general approach that does not rely on third party e-mail clients besides the default one, which is pre-installed and comes with the device itself.
Second, and most importantly, this functionality has the potential to mislead the user.
A severe downside of the URL preview is that the end of the preview is cut in case the URL is too long.
 Well-crafted URLs might thus look legitimate even though they are not because the most important part of the URL, i.e. the actual domain, was cut out.
 For example, the subdomains of the URL can be long and well-crafted so that a legitimate looking subdomain is exactly at the end of the preview.
 This will cause the user to think that the subdomain at the end of the preview is the domain of the URL.
 Ultimately, the user will trust this URL even he should not.
\item \textit{Users Click Subconsciously:} A study conducted by Karlof et al.~\cite{karlof2009conditioned} revealed that humans tend to develop automatic responses to recurring situations, so called click whirr responses, i.e. repetitively applied actions tend to happen subconsciously. Such click whirr responses include filling out forms or following links in e-mails from trusted senders. Comparing these two, carelessly filling out forms involves more actions than simply clicking on a link.
Therefore, we believe it is even more difficult to break the habit of clicking on links compared to re-thinking the action of filling out a form.
In conclusion, we do not believe that we can hinder users from clicking on links, but we hope that we can make them re-think their decision of providing their sensitive data to a potentially malicious website.
\end{enumerate}
The after click scenario does not exhibit all these drawbacks which is why we chose to follow this approach.
On the other hand, this scenario might suffer from potential malicious downloads and providing information to the phisher (benefits of before click scenario).
If a user confirms his e-mail address to the phisher by clicking on a link, further attacks towards this e-mail address are likely to follow.
Also, the pure request and displaying of a phishing website might provide additional information to the phisher or even expose the user to attacks.
For now, these aspects remain open for further research, as there is no possibility in our target scenario to detect the actual destination of a link before clicking on it.

	\item[Considered Browser:] The user is only taught browser skills which can be transferred to any other browser.
Nevertheless, when the user gets browser screenshots, for example, we made use of the Android standard browser to be sure that most users are familiar with the pictures they are shown.
\end{description}	

%===========================================
\subsection{System Requirements}
%===========================================
\label{s:sys_requirements}
Several system requirement have to be met in order to be able to install and play with the final app.
In the following we list these requirements.


\begin{description}[leftmargin=0cm]
	\item[Android:] Currently the mobile phone market is split between two major competitors. Android~(81.0\%) and iOS~(12.9\%)~\cite{androidiosmarketshare}. 
	We decided to develop an app for the Android operating system as it has more users. Moreover, we believe we have greater freedom here compared to an iOS app. 
 	Android is an open operating system and imposes less requirements and barriers that allow us a quick development and publication of our app~\cite{publishios, publishandroid}. 
	\item[Version:] Our initial intention was to develop an Android app for version 4.0 and upward.
 However, during the app development we encountered that about 24\% of all Android users still have Android 2.3.3 to 2.3.7~\cite{versionsandroid}. For this reason, we decided to modify the code so that these users can also install and use our app.
	\item[Samsung Galaxy S3 or S4:] It is not necessarily required to install the app on Samsung Galaxy S3 or S4 devices. 
Yet, we did not have the possibility to test our app (design and functionality) on different devices.
The above mentioned devices are those we tested and used for our final user study.
\end{description}

%===========================================
\subsection{Assumptions}
\label{s:assumptions}
%===========================================
We have to make some assumptions about the user's system. 
If one or more of these do not hold the user might not be able to detect that he is a target of an attack, disregarding of his skills.
In the following these assumptions are briefly explained.
\begin{description}[leftmargin=0cm]
	\item[Secure DNS:] We have to assume that DNS is not under the control of the attacker.
	Our approach is to show the user how to identify phishing attempts by analyzing the URL of the shown page.
	In fact, this is of no use if the phisher can control the DNS of the user.
	Therefore, we assume local host files and all used DNS servers as untouched by a potential attacker.
	We are aware that there exist technical approaches to secure DNS (for example, DNSSEC). However, as these are neither mandatory nor used on the majority of domains we cannot take them into consideration.
	\item[Secure Smartphone:] We imply that the user's system is in a secure state.
	This means that the attacker is not able to, for example, exploit browser vulnerabilities, replace the browser or read the user's input.
	\item[Secure SSL:] 
	For a man-in-the-middle it is possible to intercept sent or received data and to collect the user data directly without notice.
	Therefore, we warn the user against entering personal data on non-HTTPS pages.
	For this reason, we have to assume that HTTPS or the cryptography used by SSL is not broken.
\item[No Malware:] 
	Sending e-mails with malicious attachments or links to malicious downloads is a form of malware based phishing.
	In our approach we assume that the attacker does not lure the user into downloading such malicious software, which captures the user's confidential data.
	We focus on attacks where the user is encouraged to actively provide his sensitive data himself.
	Yet, we believe that preventing users from being lured into downloading malware is an important aspect.
	Therefore, in the future our approach should be expanded with regard to this problem.
\end{description}

%===========================================
\subsection{Limitations of Our Approach}
%===========================================
In addition to the general assumptions pointed out in the previous section, there are limitations of our approach resulting from the chosen target group for our app.
As described in \autoref{s:target_group}, users from our target audience are no computer experts and have neither time nor are they willing to analyze the shown website thoroughly before entering data.
Therefore, we do not intend to tell the users about possible attacks that only experienced user might find.
\begin{description}[leftmargin=0cm]
	\item[Cross-Site Scripting:]
	Cross-Site Scripting (XSS) is an attack where the attacker enters code, such as a form, into a legitimate webpage.
	For a later viewer of this page this form seems to be legitimate content of the attacked webpage and he might be deluded into entering personal data in this area. 
	Depending on the attacked webpage this cannot be detected by the user.
	This is a vulnerability of the attacked webpage and can be prevented by checking user input.
	Therefore, we think that preventing this attack is in the responsibility of the website owner.
	\item[URL Hiding Techniques:]
	As outlined in \autoref{s:antiphishing_on_smartphone} most address bars in smartphones are generally hidden and reappear only in case the user scrolls up to the top of the website.
	There is a possible attack where the attacker can prevent the user from scrolling all the way up and instead might display a fake address bar with a valid looking URL.
	A problem that the attacker has to face is that mobile browsers look very diffently which must be reflected by the fake address bar, a tedious and difficult task.
	We are aware that such techniques can be exported to a phishing toolkit, sold and used by many phishers. However, attackers do not need such sophisticated attacks yet, because enough users fall for the simple ones these days. 
	We think this is the reason why this kind of attack has not yet been observed in the wild and the reason why we do not consider it as well.
Also, this is an issue which can be addressed with the user interface with approaches similar to the iOS7 Safari browser (cf. \autoref{s:antiphishing_on_smartphone}).
\end{description}
We do not teach users regarding these types of phishing. However, we plan to design our app in such a way that these extensions will be easy to realize.